\documentclass[12pt]{article}
\usepackage[letterpaper]{geometry}
\usepackage{setspace}
\geometry{top=1in, bottom=1in, left=1in, right=1in}
\onehalfspacing

\makeatletter
\def\@maketitle{%
  \newpage
  \null
  \vskip 2em%
  \begin{center}%
    {\large
        \begin{tabular}[t]{c}%
        \@author
        \end{tabular}\par}%
  \let \footnote \thanks
    {\LARGE \@title \par}%
    %{\large \@date}%
  \end{center}%
  \par
  \vskip 1.5em}
\makeatother

\title{Statement of Purpose}
\author{Mark Kim}

\begin{document}
\maketitle

My life story is one that contains many surprising turns which is the basis for
a rich and diverse history that forms my identity.  Growing up, I had parents
whose well-intentioned but punitive attempts at improving my academic
performance led to my deep resentment of scholarly pursuits.  Unfortunately, as
a result, I found myself floundering in school despite possessing a healthy
curiosity for all things.  I had a suspicion that I was interested in STEM
subjects and could succeed in a STEM field but lacked the self-awareness and
personal fortitude to succeed in school.  This continued through early childhood
into adulthood and resulted in my withdrawal from university for a time.

After withdrawing from school, I spent the following years working and
eventually owning and managing multiple businesses ranging from retail printing
to food service.  In those years, I learned much about iterative processes:
planning, analysis, implementation, testing, and evaluation.  As a business
owner, these tools were my bread and butter; without leveraging them
consistently, my business would suffer so they also became constant ritual of mine.
Over time, however, I had come to recognize that my true interests and
passions did not align with my businesses and the markets they were operating
in. Nevertheless, it was exactly this entrepreneurial expedition that helped me
develop a broad set of skills and rediscover my past strengths.  Those years in
business made me cognizant of the emergence of big data which rekindled my natural
inquisitiveness and motivated me to enter back into scholastics with a newfound
passion and the personal tools to succeed.

With that rise of big data, it became evident to me that bad actors were using
it to exploit our primitive impulses to subsequently compel us towards decisions
and actions that benefit them alone.  This led me to wonder if we could leverage
these technologies in constructive ways to improve our lives.  My own experience
of being adrift from insufficient self-awareness and my subsequent return to
school, motivated me to learn what inspires such change.  Can these tools be
used to discern the unknown factors that inform and incite life-(re)defining
transformation?  I wanted to comprehend how people find their interests and
passions and the hidden drivers that move them towards that end.  Furthermore, I
aspired to find out if it was possible to help people affect positive change in
their own lives.

Since my re-entry into academia, my goals have not changed significantly, but my
roadmap has. As is common in any journey, I explored different paths, each
contributing to and honing my interests while also preparing me for doctoral
study.  My early research experience in Statistics and then Mathematics pedagogy
allowed me to recognize a latent appetite for research.  I also quickly understood
that a strong foundation of Mathematics would better prepare me for the type of
research that I wanted to perform, so I added it as a second major to my Computer
Science degree.  In the following years, I aggressively sought out any
and all opportunities that might be related to my research
interests: an NSF REU at the University of Houston on affective
research; a research engineering internship that investigated
clustering of phishing emails; leading an early exposure to artificial
intelligence program for college first year students; and a research project
using large language models for student advising.  Upon completing my bachelors
degree, I advanced to a Data Science and Artificial Intelligence
masters program to bridge the gap towards a doctoral degree.  

As I have been exposed to more research and teaching opportunities, my
determination to pursue and succeed in a doctoral program has only increased.
But my progress towards
academia is still incomplete. The SEO Fellowship program would provide me with
resources that I never knew to search for.  In addition to the resentment I felt
in my youth, I falsely learned that life was a solitary pursuit that was devoid
of support.  With guidance from peers and faculty mentors, I have come to
recognize that seeking out assistance is not a weakness; instead, it is a means
for accelerated edification and broadened perspective.  Likewise, I have also
learned that sharing such kindness with others is deeply rewarding. While research has
captivated my interests, I have found that teaching has become my greatest
ambition.  I believe that the SEO Fellowship would bolster the aid that
has already been graciously offered to me which would enable me to further
develop my passions.
\end{document}