\documentclass[12pt]{article}
\usepackage[letterpaper]{geometry}
\usepackage{setspace}
\geometry{top=0.5in, bottom=0.5in, left=0.5in, right=0.5in}
\doublespacing

\title{CS Graduation Speech}

\begin{document}
\textbf{Thank you} Dr. Puder for that gracious introduction...

Distinguished faculty, staff, families, guests, and, of course, my fellow graduates,

% \textbf{We're here}!  We've done it!

\textbf{I can't} emphasize enough how much of an honor it is for me to be standing here
before you today to deliver this address.  When I first arrived here at San
Francisco State, I never could have imagined that I would be up here at this lectern.

\textbf{To be} completely honest, I was not even entirely sure that I would ever
wear the cap and gown that signifies our passage from university student to graduate.
The reason for this is that I have attempted this endeavor before but failed
miserably and the fear of repeating that past has haunted me.

\textbf{Despite this}, I was determined to try... And try I did.  Along this path, I
encountered others who were facing many of the same challenges.

\textbf{They struggled} through a lot of the same classes. My fellow graduates know
what I mean...hunting down that one line of code that was causing your program to
misbehave out of hundreds or thousands of lines.  This speech would not be
complete if I did not mention the one course that exemplifies this task
better than any other: Operating Systems and
the File System project.  What would life have been like without it?  Fewer
segmentation faults, for sure.

\textbf{Many of us} experienced or were witness to, tears shed at night from
stress or frustration originating from these types of project or exams...or sometimes just from a
particularly difficult day.  And oooohhh yes...we had many difficult days... 

\textbf{Let us} not forget the disruptive force of the pandemic... I remember enduring the
whiplash of shifting from in-person classes to the isolation of our
homes, staring at a grid of black boxes with mere names attached.  Then just as
we were getting used to it, we found ourselves on campus again, forced to
transition back.  These were indeed unprecedented times, clichéd as it may sound.

\textbf{In the midst of} all this I was trying to find a community to fit into.
But what I did not realize was that this \emph{\textbf{is}} the
community I was seeking.  I was not \emph{finding} community but \emph{building} it.  And
I was not doing it alone.  The people whom I now call friends were building it with
me.  Furthermore, it did not consist of only fellow students.  It also included
faculty, staff, and alumni.

\textbf{It is with} the tremendous support and encouragement of this community
that has brought me here before you today.  Thank you to the professors that
believed in me and encouraged me throughout my time here, to my brother for his understanding
during difficult times, and to my dear friends who supported me when I felt
defeated, all of whom make up this community I speak of.

\textbf{But our stories} do not end here, my fellow graduates. As we turn this new page and continue
writing our stories, let us embrace the lessons we have learned during our time
here. Each of us has faced our own unique set of obstacles, but we have overcome them with
resilience, determination, and the unwavering support of our community. 

\textbf{Remember the late-night} study sessions, the collaborations, and the
moments of triumph when we finally completed a project successfully or aced a challenging exam.
Those experiences have shaped us into the individuals we are today. 

\textbf{As we move forward}, let us not forget the importance of community. It was
here, within these lecture halls, virtual classrooms, and the CS Lab
that we attained not just knowledge, but built a network of support and friendship. The
bonds we formed with our fellow students, and the guidance, mentorship and wisdom we
received from our dedicated faculty, have all contributed to our growth and success. 

\textbf{Now, as we embark} on new enterprises and explore uncharted territories, let us
carry the spirit of community with us. Let us reach out to those in need, uplift
others with our words and actions, and create inclusive spaces where everyone
feels valued and heard. Let us continue to build the communities we seek, not
just for ourselves but for those who will follow in our footsteps. 

\textbf{As we face} the challenges that lie ahead, whether it be in our careers, further
studies, or personal endeavors, let us remember the resilience we have
cultivated during this strange era. We have proven that we can adapt,
innovate, and overcome any obstacle that comes our way. We have the power to
make a positive impact on the world and shape a future that reflects our shared
values. 

\textbf{So, my fellow graduates}, as we close this chapter and ink the next pages
of our lives, let us do so with a sense of purpose, courage, and gratitude. Let
us never forget the honor it has been to stand here today, and may our journeys
be filled with endless possibilities, remarkable achievements, and the joy of
making a difference. 

Congratulations, Class of 2023!
\end{document}