\documentclass[12pt]{article}
\usepackage[letterpaper]{geometry}
\usepackage{setspace}
\geometry{top=0.5in, bottom=0.5in, left=0.5in, right=0.5in}
\doublespacing

\title{CAHSI Scholars Essay}
\author{Mark Kim}

\begin{document}
\maketitle
% Include section headings in your essay: Past Efforts, Future Efforts, and
% Reflection. Ensure the essay does not exceed 750 words. It is recommended you
% dedicate 250 words for each section of your essay.  

% To write your essay response consider the following:   

% Past Efforts: What have you done to better yourself, to support others, and to
% advance the community? 

\section*{Past Efforts}

%         Engagement with CAHSI: Select two or three CAHSI-sponsored
%         opportunities or practices in which you have been engaged that has
%         positively impacted your development as a learner or leader. Identify
%         the opportunity/practice and briefly describe your engagement. How did
%         engagement in this opportunity or practice impact you?  
I have only participated in one CAHSI-sponsored opportunity: the Great Minds in
STEM conference in 2022.  Throughout this conference, I was exposed to many
different possibilities in STEM and the influence that CAHSI has on the
community of Hispanic students.  Having participated in the various workshops, I
began to understand the importance of diversity in computing and beyond.
Through this experience, I became even more dedicated to providing additional
support for students that may be under-represented or lacking in financial
means.

%         Community Outreach: Describe meaningful direct service to your
%         community that you have undertaken during your academic career. State
%         whether service work was independent or sponsored by another entity,
%         your motivation for entering service work, names of
%         organization/community being served, length of service, frequency of
%         service, and outcomes/outputs of service.
The primary method with which I directed my efforts was through our Association
for Computing Machinery (ACM) Student Chapter.  As president of the organization in
the 2022-2023 academic year, I worked to do a post-COVID resuscitation.  Through
our efforts to provide additional resources for our students, we were able to
bring our active member count essentially from 0 to over 100.  My careful
planning of various weekly workshops (IDE setup and usage, Git, GitHub,
LeetCode, etc.) allowed us to provide students with skills that are not
generally taught formally in school and create a community for students of all
backgrounds.

%         Co-curricular activities: List and briefly explain the activities
%         outside of required coursework for your degree plan that you have been
%         involved with during your college/graduate career. Include leadership
%         positions.
Outside of ACM, I also participated in the Supplemental Instruction program as a
Facilitator, where I taught companion courses that paired with foundational
introductory courses in Mathematics and Computer Science.  Each lesson I created
was designed to deliver a deeper understanding of difficult concepts.  These
lessons were presented by a mini-lecture followed by exercises meant to
challenge students and prepare them for subsequent subjects.  These courses were
especially valuable for students that may not have had the luxury of being
exposed to such advanced studies.  I also found myself 

% Future Efforts: What plans or strategies do you plan to do to positively
% impact the recruitment, retainment, and advancement of Hispanics in computing? 

% Reflection: What have you learned about yourself since being engaged with
% CAHSI or other activities? 

%     What would you do differently to improve opportunities or practices geared
%     towards student success that you have participated in, or observed? 

%     What kind of culture have you created, or do you hope to create in your
%     learning and/or work environment? Consider efforts that span from small to
%     sizable financial investment, as well as efforts that require short to
%     longer term time investment. 

%     What would you do differently to improve opportunities or practices geared
%     towards student success that you have participated in, or observed?


\end{document}